---
title: R Markdown doc
author: Jing Ma
date: '2023-03-14'
slug: rmarkdown-doc
categories:
  - R
tags:
  - doc
  - R Markdown
description: A brief document of R Markdown doc.
toc: true
# output:
#   blogdown::html_page:
#     toc: true
# #     fig_width: 6
# #     # dev: "svg"
draft: true
---

> 当我们行走，要努力与世界相处
>
>> 当我们***盛放***，要努力与自己相处
>>> This one

# To test Rmd rendering :smile: :rabbit2:

This is a summary:

```{r orange}
summary(Orange)
```

add a plot by `ggplot2`:

```{r line, echo=FALSE}
library(ggplot2)
ggplot(Orange, aes(x = age,
                   y = circumference,
                   color = Tree)) +
  geom_point() +
  geom_line() +
  guides(color = "none") +
  theme_bw()
```

include inline math expressions in a pair of backticks `$math$`, e.g., `$S_n = \sum_{i=1}^n X_i$`. Similarly, math expressions of the display style have to be written in `$$math$$`

For .Rmd posts to be rendered to .html,you can use $math$ for inline math expressions, and $S_n = \sum_{i=1}^n X_i$ $$math$$ for display-style expressions.[^1]

[^1]: This is a footnote

`math`, `S_n = \sum_{i=1}^n X_i`, `$math$`

## List page

<http://localhost:4321/post/>


## Terms: tag & category

- <http://localhost:4321/tags/>
- <http://localhost:4321/categories/>
- <http://localhost:4321/tags/running/>
- <http://localhost:4321/tags/r-markdown/>
- <http://localhost:4321/categories/blog/>
- <http://localhost:4321/categories/r/>

## Fetch data

http://localhost:4321/data/marathons.json

## A blockquote

> Serving the directory . at http://localhost:4321. Launched the hugo server in the background (process ID: 6646). To stop it, call blogdown::stop_server() or restart the R session.
Rendering content/post/2023-03-14-rmarkdown-test/index.Rmd... Done.

> Serving the directory . at http://localhost:4321.
> Launched the hugo server in the background (process ID: 6646). To stop it, call blogdown::stop_server() or restart the R session.
> Rendering content/post/2023-03-14-rmarkdown-test/index.Rmd... Done.

>   Serving the directory . at http://localhost:4321.
>   Launched the hugo server in the background (process ID: 6646). To stop it, call blogdown::stop_server() or restart the R session.
>   Rendering content/post/2023-03-14-rmarkdown-test/index.Rmd... Done.

> Serving the directory . at http://localhost:4321.
>
> Launched the hugo server in the background (process ID: 6646). To stop it, call blogdown::stop_server() or restart the R session.
>
> Rendering content/post/2023-03-14-rmarkdown-test/index.Rmd... Done.
